---
title: "Modeling Paris Paintings"
author: "Rami Sbahi"
date: "February 25, 2020"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Getting started

1. Clone your repo `appex07-[github_name]` to create a new project
   in RStudio Cloud under the STA 199 class space.

2. Configure git
      ```{r config-git-ex, eval=FALSE}
      library(usethis)
      use_git_config(user.name="your name", user.email="your email")
      ```

# Packages and Data

```{r packages}
library(tidyverse)
library(broom)
```

```{r load-data, message=FALSE}
paris_paintings <- read_csv("data/paris_paintings.csv", 
                            na = c("n/a", "", "NA"))

?paris_paintings
```

# Tasks

## Task 1

Fit a multiple linear regression model with the following main effects: 
`lrgfont`, `Height_in`, `Width_in`, and `relig`.

Interpret each of the estimated model coefficients.

```{r multiple-reg}
m_main <- paris_paintings %>%
  lm(log(price) ~ factor(lrgfont) + Height_in + Width_in + factor(relig), data = .)

m_main %>%
  tidy() %>%
  mutate(exp_estimate = exp(estimate)) %>%
  select(term, estimate, exp_estimate)
```

Non-religious paintings without a large font, with a surface are of 0 square 
inches, are expected to have a price of $98.65.

All else held constant, painting with a large font is expected, on average, to 
have a log(price) 2.572 greater than one without.

All else held constant, a religious painting is expected, on average, to have a 
log(price) 0.519 less than one which isn't.

All else held constant, for every additional inch in height, log(price) is 
expected, on average, to decrease by 0.00856.

All else held constant, or every additional inch in width, log(price) is 
expected, on average, to increase by 0.021.


## Task 2

Fit a multiple linear regression model with main effects for 
`Height_in` and `lrgfont`, as well as their interaction.

What is the model equation for paintings where the dealer devotes an 
additional paragraph? How about for paintings where the dealer does NOT devote 
an additional paragraph?

```{r interaction}
m_int <- lm(log(price) ~ Height_in + lrgfont + Height_in*lrgfont, data = paris_paintings)

m_int %>%
  tidy() %>%
  select(term, estimate)
```

Total equation:
$$\widehat{\mbox{log(price)}} = 4.676 + 0.00511~\mbox{Height_in} + 
2.172~\mbox{lrgfont} + 0.0185 * \mbox{Height_in} * \mbox{lrgfnt}$$

Additional paragraph (assuming this means lrgfont = 1)
$$\widehat{\mbox{log(price)}} = 6.848 + 0.02361~\mbox{Height_in}$$

No additional paragraph (assuming this means lrgfont = 0)
$$\widehat{\mbox{log(price)}} = 4.676 + 0.00511~\mbox{Height_in}$$

# Submission

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.